---
title: "Mani_Timelapse_CF"
author: "MANISHA"
date: "`r Sys.Date()`"
output: 
  html_document: 
    code_folding: hide
    fig_caption: yes
    fig_height: 6
    fig_width: 12
    fontsize: 10pt
    toc: true
    toc_float: true
    self_contained: false
---

# Load the config

In this file there is experiment that is analysed.
- Confocal imaging based.


This experiments was performed by Manisha in FV10i as first trial for live cell imaging.
apart.


```{r, eval=TRUE, message=FALSE, warning=FALSE}
library(magrittr)
library(dplyr)
library(ggplot2)
source("R/ggtheme_jack.R")
source("R/fun_multiplot.R")
ggplot2::theme_set(theme_jack())

layouts <- "TRUE"
cell_traces <- "TRUE"
fit_plots <- "TRUE"
Diagnosis <- "TRUE"
filtering <- "TRUE"
base_path <- c("../../../data/170427_thp1_h37ra_a21_tl")

exp_name <- 
  c(
    "Image_01_01_01_01.oif.files_output",
    "Image_01_02_01_01.oif.files_output",
    "Image_01_03_01_01.oif.files_output",
    "Image_02_01_01_01.oif.files_output",
    "Image_02_02_01_01.oif.files_output",
    "Image_02_03_01_01.oif.files_output",
    "Image_03_01_01_01.oif.files_output",
    "Image_03_02_01_01.oif.files_output",
    "Image_03_03_01_01.oif.files_output"
  )


exp_read_out <- c("Cells", "Image")

dat <- list(list())
for(i in 1:length(exp_name)){
  dat[[i]] <- 
    readr::read_csv(
      sprintf("%s/%s/%s.csv",
              base_path,
              exp_name[i],
              exp_read_out[1])
    )
}

dat %<>% bind_rows()
dat %<>% tbl_df()
```

# Aim 

The experiment aims to determine the changes in the lysosomal number and intensities upon infection of H37Ra in THP1 cells with time.
The second aim is to check the effect of compound a21(naproxen) on lysosomal pathway upon infection with time.

There are three samples - uninfected, infected, infected (Metadata_Inf_Status) & untreated, untreated, treated (Metadata_Treatment, Metadata_Compound)

- There are three sites in each sample - 1,2,3 (Metadata_Sample)

- There are 79 timepoints for each site at  10 minutes each (Metadata_Site)

- There are 4 Z-slices of 1 micron thickness for each site and each timepoint (Metadata_ZSlice)

- The tracking id is for each cell (Trackobjects_Label_50)

We will sum up the values for z slices for each cell tracked.

Analysis Method -

1. We can fit the curves of each cell tracked - median fit or best fit
2. We can take the mean, median, stdev,mad etc for the lysosomal features in each condition and compare it.



## Join Layouts

```{r, message=FALSE, eval=layouts}

exp_layout <-
  readr::read_csv(
    sprintf("%s/170427_thp1_h37ra_a21_tl.csv", base_path)
    ) %>%
  tbl_df()

dat$Metadata_Sample %<>% as.numeric()
dat$Metadata_Site %<>% as.numeric()

dat %<>%
  inner_join(exp_layout, .)

dat %<>%
  select(
    contains("Metadata"),
    contains("Children"),
    contains("AreaShape_Area"),
    contains("Label_50"),
    contains("Intensity_IntegratedIntensity"),
    contains("Object_Number")
    )

dat %<>% 
  select(
    -contains("Edge"), 
    -contains("Frame"), 
    -contains("Channel"),
    -contains("Series"),
    -contains("FileLocation")
    )


colnames(dat) <- gsub("_50", "", colnames(dat))

```

### Timepoints cleaning uup

```{r, message=FALSE, eval=filtering}

dat$Metadata_Time <- gsub("T001", "000", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T002", "010", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T003", "020", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T004", "030", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T005", "040", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T006", "050", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T007", "060", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T008", "070", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T009", "080", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T010", "090", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T011", "100", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T012", "120", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T013", "130", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T014", "140", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T015", "150", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T016", "160", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T017", "170", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T018", "180", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T019", "190", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T020", "200", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T021", "210", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T022", "220", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T023", "230", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T024", "240", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T025", "250", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T026", "260", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T027", "270", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T028", "280", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T029", "290", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T030", "300", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T031", "310", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T032", "320", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T033", "330", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T034", "340", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T035", "350", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T036", "360", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T037", "370", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T038", "380", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T039", "390", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T040", "400", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T041", "410", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T042", "420", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T043", "430", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T044", "440", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T045", "450", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T046", "460", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T047", "470", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T048", "480", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T049", "490", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T050", "500", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T051", "510", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T052", "520", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T053", "530", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T054", "540", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T055", "550", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T056", "560", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T057", "570", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T058", "580", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T059", "590", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T060", "600", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T061", "610", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T062", "620", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T063", "630", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T064", "640", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T065", "650", dat$Metadata_Time)
dat$Metadata_Time <- gsub("T066", "660", dat$Metadata_Time)


dat$Metadata_Time %<>% as.numeric()

dat %<>% filter(Metadata_Time < 665)

```



# Diagnostic plots without filtering

```{r, fig.width=10, fig.height=8, eval=Diagnosis}
p1 <- dat %>% ggplot(aes(Mean_Nuclei_AreaShape_Area)) + geom_density() + xlim(0,2500)
p2 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_RescaledDAPI)) + geom_density() + xlim(0,10000)
p3 <- dat %>% ggplot(aes(Children_BCG_Count))+geom_density()+ xlim(0,20)
p4 <- dat %>% ggplot(aes(Mean_BCG_AreaShape_Area))+geom_density()+ xlim(0,85)
p5 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_FilteredGCH))+geom_density()+ xlim(0,2500)


p6 <- dat %>% ggplot(aes(Children_RCH_Count))+geom_density() + xlim(0,70)
p7 <- dat %>% ggplot(aes(Mean_RCH_AreaShape_Area)) + geom_density() + xlim(0,80)
p8 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_FilteredRCH)) + geom_density() + xlim(0,3000)

multiplot(p1,p2,p3,p4,p5,p6,p7,p8, cols = 4)
```

# Filtering

```{r, message=FALSE, fig.width=5, fig.height=4, eval=filtering}

n1 <- nrow(dat)

dat %>%
  ggplot(aes(Intensity_IntegratedIntensity_RescaledDAPI)) + 
  geom_density() +
  geom_vline(aes(xintercept=200)) + 
  geom_vline(aes(xintercept=8000))

dat %<>% 
  filter(Intensity_IntegratedIntensity_RescaledDAPI > 200 & Intensity_IntegratedIntensity_RescaledDAPI < 8000)
n2 <- nrow(dat)


dat %>% 
  ggplot(aes(Mean_Nuclei_AreaShape_Area)) +
  geom_density() +
  geom_vline(aes(xintercept=100)) +
  geom_vline(aes(xintercept=1250))

dat %<>% 
  filter(Mean_Nuclei_AreaShape_Area < 1250 & Mean_Nuclei_AreaShape_Area > 100)

n3 <- nrow(dat)


n1
n2
n3

cells_filtered <- (n1-n3)*100/n1

sprintf("Percentage of cells filtered out: %s", cells_filtered)

```

# Diagnostic plots after filtering

```{r, fig.width=10, fig.height=8, eval=Diagnosis}
p1 <- dat %>% ggplot(aes(Mean_Nuclei_AreaShape_Area)) + geom_density() + xlim(0,2500)
p2 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_RescaledDAPI)) + geom_density() + xlim(0,10000)
p3 <- dat %>% ggplot(aes(Children_BCG_Count))+geom_density()+ xlim(0,20)
p4 <- dat %>% ggplot(aes(Mean_BCG_AreaShape_Area))+geom_density()+ xlim(0,85)
p5 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_FilteredGCH))+geom_density()+ xlim(0,2500)


p6 <- dat %>% ggplot(aes(Children_RCH_Count))+geom_density() + xlim(0,70)
p7 <- dat %>% ggplot(aes(Mean_RCH_AreaShape_Area)) + geom_density() + xlim(0,80)
p8 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_FilteredRCH)) + geom_density() + xlim(0,3000)

multiplot(p1,p2,p3,p4,p5,p6,p7,p8, cols = 4)
```

# labelling the infection status

```{r,  message=FALSE, eval=layouts}

unique(dat$Metadata_InfStatus)

dat$Metadata_InfStatus <- gsub("H37Ra", "INF", dat$Metadata_InfStatus)
dat$Metadata_InfStatus <- gsub("Uninf", "NI", dat$Metadata_InfStatus)

unique(dat$Metadata_InfStatus)

dat$Metadata_InfStatus[dat$Children_BCG_Count < "1" & dat$Metadata_InfStatus == "INF"] <- "Bystander"

unique(dat$Metadata_InfStatus)

dat$Metadata_InfStatus <-
  factor(dat$Metadata_InfStatus, levels=c('NI','Bystander','INF'))

```

# Grouping the zslices

```{r,  message=FALSE, eval=layouts}

meta_cols <- dat %>% select(contains("Metadata")) %>% names()
feat_cols <- dat %>% select(-contains("Metadata"), -TrackObjects_Label) %>% names()

dat_mean <-
  dat %>%
  group_by(
    Metadata_Sample,
    Metadata_Site,
    Metadata_Time,
    Metadata_InfStatus,
    Metadata_Treatment,
    Metadata_Compound,
    TrackObjects_Label) %>%
  dplyr::summarize_each_(funs(mean(., na.rm=TRUE)),
                         vars = feat_cols)

dat_sum <-
  dat %>%
  dplyr::group_by(
    Metadata_Sample,
    Metadata_Site,
    Metadata_Time,
    Metadata_InfStatus,
    Metadata_Treatment,
    Metadata_Compound,
    TrackObjects_Label) %>%
  dplyr::summarize_each_(dplyr::funs(sum(., na.rm=TRUE)),
                         vars = feat_cols)

```

# Filtering Single track label cells

```{r,  message=FALSE, eval=layouts}


fat <- 
  dat %>% 
  group_by( 
  Metadata_Sample,
  Metadata_Site,
  Metadata_Time,
  Metadata_InfStatus,
  Metadata_Treatment,
  Metadata_Compound,
  Metadata_Zslice,
  TrackObjects_Label
  ) %>% count() %>%
  filter(n == 1) %>%
  select(-n)

dat1 <- inner_join(fat,dat)

```




##Plotting data

# Single cell traces

Imaging done per 10 minute for eleven hours

```{r, fig.width=12, fig.height=16, warning=FALSE, eval=cell_traces}

ggplot(dat1,
       aes(
         x = Metadata_Time,
         y = Intensity_IntegratedIntensity_RescaledRCH,
         color = Metadata_Zslice,
         group = TrackObjects_Label)) +
  geom_line(alpha=0.5) + theme(legend.position="none") +
  facet_grid(Metadata_Site + Metadata_Zslice ~ Metadata_Treatment + Metadata_InfStatus)

```



# Ploting changes in lysotracker content in cell over time

```{r, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, eval=TRUE}
feat_cols <- c("Intensity_IntegratedIntensity_RescaledRCH")

dat_med <-
  dat1 %>%
  dplyr::group_by(
    Metadata_Time,
    Metadata_InfStatus,
    Metadata_Treatment) %>%
  dplyr::summarize_each_(dplyr::funs(mean(., na.rm=TRUE)),
                         vars = feat_cols)

p1 <-
  ggplot(dat1,
         aes(
           x = Metadata_Time,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_smooth()+
  facet_grid( ~ Metadata_Treatment) +
  labs(
    title="Fitted Kinetics of lysotracker after 0 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Time (in minutes)")
p2 <-
  ggplot(dat_med,
         aes(
           x = Metadata_Time,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_smooth()+
  facet_grid( ~ Metadata_Treatment)+
  labs(
    title="Median Collapsed Kinetics of lysotracker after 0 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Time (in minutes)")

multiplot(p1, p2, cols=1)

```



# Ploting changes in lysotracker content in cell over time without unexposed

```{r, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, eval=TRUE}
feat_cols <- c("Intensity_IntegratedIntensity_RescaledRCH")

dat_med <-
  dat1 %>%
  dplyr::group_by(
    Metadata_Time,
    Metadata_InfStatus,
    Metadata_Treatment,
    Metadata_Zslice) %>%
  dplyr::summarize_each_(dplyr::funs(mean(., na.rm=TRUE)),
                         vars = feat_cols)

p1 <-
  ggplot(dat1 %>% filter(Metadata_InfStatus !="NI"),
         aes(
           x = Metadata_Time,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_smooth()+
  facet_grid( ~ Metadata_Treatment) +
  labs(
    title="Fitted Kinetics of lysotracker after 0 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Time (in minutes)")
p2 <-
  ggplot(dat_med %>% filter(Metadata_InfStatus !="NI"),
         aes(
           x = Metadata_Time,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_smooth()+
  facet_grid( ~ Metadata_Treatment)+
  labs(
    title="Median Collapsed Kinetics of lysotracker after 0 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Time (in minutes)")

multiplot(p1, p2, cols=1)

```

# Ploting changes in lysotracker content in cell over time without unexposed and treatment

```{r, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, eval=TRUE}
feat_cols <- c("Intensity_IntegratedIntensity_RescaledRCH")

dat_med <-
  dat1 %>%
  dplyr::group_by(
    Metadata_Time,
    Metadata_InfStatus,
    Metadata_Treatment,
    Metadata_Zslice) %>%
  dplyr::summarize_each_(dplyr::funs(mean(., na.rm=TRUE)),
                         vars = feat_cols)

p1 <-
  ggplot(dat1 %>% filter(Metadata_InfStatus !="NI" && Metadata_Treatment !="Treated"),
         aes(
           x = Metadata_Time,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_smooth()+
  labs(
    title="Fitted Kinetics of lysotracker after 0 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Time (in minutes)")
p2 <-
  ggplot(dat_med %>% filter(Metadata_InfStatus !="NI" && Metadata_Treatment !="Treated"),
         aes(
           x = Metadata_Time,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_smooth()+
  labs(
    title="Median Collapsed Kinetics of lysotracker after 0 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Time (in minutes)")

multiplot(p1, p2, cols=1)

```


# Ploting changes in lysotracker content in cell at time intervals of 2hrs as boxplot - without treatment

```{r, message=FALSE, warning=FALSE, fig.width=12, fig.height=8, eval=TRUE}

feat_cols <- c("Intensity_IntegratedIntensity_RescaledRCH")


time_point <- c("60" , "180", "300", "420", "540", "660")

n1 <- ggplot(dat1 %>% filter(Metadata_InfStatus !="NI" && Metadata_Time == time_point[1]),
         aes(
           x = Metadata_InfStatus,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 1 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Infection status at Time (in minutes)")


n2 <- ggplot(dat1 %>% filter(Metadata_InfStatus !="NI" && Metadata_Time == time_point[2]),
         aes(
           x = Metadata_InfStatus,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 3 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Infection status at Time (in minutes)")

n3 <- ggplot(dat1 %>% filter(Metadata_InfStatus !="NI" && Metadata_Time == time_point[3]),
         aes(
           x = Metadata_InfStatus,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 5 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Infection status at Time (in minutes)")

n4 <- ggplot(dat1 %>% filter(Metadata_InfStatus !="NI" && Metadata_Time == time_point[4]),
         aes(
           x = Metadata_InfStatus,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 7 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Infection status at Time (in minutes)")

n5 <- ggplot(dat1 %>% filter(Metadata_InfStatus !="NI" && Metadata_Time == time_point[5]),
         aes(
           x = Metadata_InfStatus,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 9 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Infection status at Time (in minutes)")

n6 <- ggplot(dat1 %>% filter(Metadata_InfStatus !="NI" && Metadata_Time == time_point[6]),
         aes(
           x = Metadata_InfStatus,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 11 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Infection status at Time (in minutes)")



multiplot(n1,n2,n3,n4,n5,n6, cols=3)

```


# Ploting changes in lysotracker content in cell at time intervals of 2hrs as boxplot

```{r, message=FALSE, warning=FALSE, fig.width=12, fig.height=8, eval=TRUE}

feat_cols <- c("Intensity_IntegratedIntensity_RescaledRCH")


time_point <- c("60" , "180", "300", "420", "540", "660")

n1 <- ggplot(dat1 %>% filter(Metadata_InfStatus !="NI" && Metadata_Time == time_point[1]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 1 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")


n2 <- ggplot(dat1 %>% filter(Metadata_InfStatus !="NI" && Metadata_Time == time_point[2]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 3 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")

n3 <- ggplot(dat1 %>% filter(Metadata_InfStatus !="NI" && Metadata_Time == time_point[3]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 5 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")

n4 <- ggplot(dat1 %>% filter(Metadata_InfStatus !="NI" && Metadata_Time == time_point[4]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 7 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")

n5 <- ggplot(dat1 %>% filter(Metadata_InfStatus !="NI" && Metadata_Time == time_point[5]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 9 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")

n6 <- ggplot(dat1 %>% filter(Metadata_InfStatus !="NI" && Metadata_Time == time_point[6]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 11 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")



multiplot(n1,n2,n3,n4,n5,n6, cols=3)

```

# Ploting changes in lysotracker content in cell at time intervals of 2hrs as boxplot - infected cells only

```{r, message=FALSE, warning=FALSE, fig.width=12, fig.height=8, eval=TRUE}

feat_cols <- c("Intensity_IntegratedIntensity_RescaledRCH")


time_point <- c("60" , "180", "300", "420", "540", "660")

n1 <- ggplot(dat1 %>% filter(Metadata_InfStatus =="INF" && Metadata_Time == time_point[1]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 1 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")

n2 <- ggplot(dat1 %>% filter(Metadata_InfStatus =="INF" && Metadata_Time == time_point[2]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 3 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")

n3 <- ggplot(dat1 %>% filter(Metadata_InfStatus =="INF" && Metadata_Time == time_point[3]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 5 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")

n4 <- ggplot(dat1 %>% filter(Metadata_InfStatus =="INF" && Metadata_Time == time_point[4]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 7 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")

n5 <- ggplot(dat1 %>% filter(Metadata_InfStatus =="INF" && Metadata_Time == time_point[5]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 9 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")

n6 <- ggplot(dat1 %>% filter(Metadata_InfStatus =="INF" && Metadata_Time == time_point[6]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 11 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")



multiplot(n1,n2,n3,n4,n5,n6, cols=3)

```



# Ploting changes in lysotracker content in cell at time intervals of 2hrs as boxplot - uninfected bystander cells only

```{r, message=FALSE, warning=FALSE, fig.width=12, fig.height=8, eval=TRUE}

feat_cols <- c("Intensity_IntegratedIntensity_RescaledRCH")


time_point <- c("60" , "180", "300", "420", "540", "660")

n1 <- ggplot(dat1 %>% filter(Metadata_InfStatus =="Bystander" && Metadata_Time == time_point[1]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 1 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")

n2 <- ggplot(dat1 %>% filter(Metadata_InfStatus =="Bystander" && Metadata_Time == time_point[2]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 3 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")

n3 <- ggplot(dat1 %>% filter(Metadata_InfStatus =="Bystander" && Metadata_Time == time_point[3]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 5 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")

n4 <- ggplot(dat1 %>% filter(Metadata_InfStatus =="Bystander" && Metadata_Time == time_point[4]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 7 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")

n5 <- ggplot(dat1 %>% filter(Metadata_InfStatus =="Bystander" && Metadata_Time == time_point[5]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 9 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")

n6 <- ggplot(dat1 %>% filter(Metadata_InfStatus =="Bystander" && Metadata_Time == time_point[6]),
         aes(
           x = Metadata_Treatment,
           y = (Intensity_IntegratedIntensity_RescaledRCH),
           color = Metadata_InfStatus)) +
  geom_boxplot()+
  facet_grid( ~ Metadata_Time) +
  labs(
    title="lysotracker intensity at 11 hpi",
    y="Whole Cell Int-Intensity of lysotracker",
    x="Treatment at Time (in minutes)")



multiplot(n1,n2,n3,n4,n5,n6, cols=3)

```
